PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-12-19 qfenv_paper/qf_environment.tex
Final edits to draft
Still need funding info

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael R.~Blanton\altaffilmark{1}, 
John~Moustakas\altaffilmark{2},
Alison L.~Coil\altaffilmark{3}, 
Richard J.~Cool\altaffilmark{4}, 
Daniel J.~Eisenstein\altaffilmark{5},
Ramin A.~Skibba\altaffilmark{3}
Kenneth C.~Wong\altaffilmark{6}, 
Guangtun~Zhu\altaffilmark{7}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{3}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{4}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of
the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using
spectroscopic redshifts and multi-wavelength imaging data from the
PRIsm MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey
(SDSS). Our stellar mass limited galaxy sample consists of $\sim
13,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS
galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent
or star-forming based on an evolving specific star formation cut, and
as low or high density environments based on fixed cylindrical
aperture environment measurements on a volume-limited environment
defining population. For quiescent and
star-forming galaxies in low or high density environments, we examine
the evolution of their stellar mass function (SMF). Then using the
SMFs we compute $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify its
evolution within our redshift range. We find that the quiescent
fraction is higher at higher masses and in denser environments. The
quiescent fraction rises with cosmic time for all masses and
environments. At a fiducial mass of $10^{10.5}M_\odot$, from $z\sim
0.7$ to $0.1$, the quiescent fraction rises by $15\%$ at the
lowest environments and by $25\%$ at the highest environments we measure.
These results suggest that for a minority of galaxies their cessation
of star formation is due to external influences on
them. However, in the recent Universe a substantial fraction of the
galaxies that cease forming stars do so due to internal processes.
\end{abstract}

@@

Throughout the paper we assume a cosmology with $\Omega_{m} = 0.3,
\Omega_{\Lambda} = 0.7$, and $H_0 = 70 \: \rm{km} \; \rm{s}^{-1}
\rm{Mpc}^{-1}$. All magnitudes are AB-relative.

@@

In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a
brief summary of the PRIMUS data and the SDSS data used for our sample
selection. In Section \ref{sec:target} we define our stellar mass complete galaxy sample.  
Then, in Section \ref{sec:sfq}, we classify our sample galaxies as quiescent or star-forming. 
We calculate the environment
using a volume-limited Environment Defining Population in Section
\ref{sec:environment}.  Finally, in Section \ref{sec:edgeeffect}, we
account for edge effects in the surveys.

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.2}
	\plotone{fig_edp_sdss_z0_05_0_12_primus_z0_2_1_0_Mr_redshift.png}
        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top. Both samples are divided into redshift bins: $z \approx 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right). The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS. The rest contain galaxies and EDP selected from PRIMUS. The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies. Stellar mass completeness limits, specified in Section \ref{sec:target}, are imposed on the galaxy population. Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRIMUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and
spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim
120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range
$z \approx 0-1.2$. The survey was conducted using the IMACS
spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers (\citealt{Coil:2011aa, Cool:2013aa}).

While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \rm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging for a total of $\sim 5.5 \; \rm{deg}^2$ (similar to the sample selection in \citealt{Moustakas:2013aa}). Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html}): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chandra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS). The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey field (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}). Our fifth and final field is the Cosmic Evolution Survey (COSMOS\footnote{http://cosmos.astro.caltech.edu}) field. For all of our fields we have near-UV (NUV) and far-UV (FUV) photometry from the {\em GALEX} Deep Imaging Survey (DIS; \citealt{Martin:2005aa, Morrissey:2005aa}) as well as ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs. \cite{Moustakas:2013aa} provides detailed descriptions of integrated flux calculations in the photometric bands for each of our fields. Furthermore, we derive the {\em K-corrections} from the photometry using \texttt{K-correct} (v4.2; \citealt{Blanton:2007aa}).

Finally, using the spectroscopic redshift and broad wavelength photometry we apply \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies (\citealt{Moustakas:2013aa}). \texttt{iSEDfit} uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}. For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \rm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SDSS-GALEX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SDSS-GALEX} \label{sec:sdss}
At low redshifts, we use spectroscopic redshifts and $ugriz$ photometry from the SDSS Data Release 7 (DR7; \citealt{Abazajian:2009aa}). More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (hereafter VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\citealt{Blanton:2005aa}). We further restrict the VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \rm{ks}$ from {\em GALEX} Release 6. This leaves $167,727$ galaxies.

Next, we use the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diameter search radius, to obtain the NUV and FUV photometry for the SDSS-{\em GALEX} galaxies. For optical photometry, we use the $ugriz$ bands from the SDSS \texttt{model} magnitudes scaled to the $r$-band \texttt{cmodel} magnitude. These photometric bands are then supplemented with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \citealt{Jarrett:2000aa}) and with photometry at $3.4$ and $4.6 \mu \rm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}. Further details regarding the SDSS-{\em GALEX} sample photometry can be found in Section 2.4 of \cite{Moustakas:2013aa}. As previously done on the PRIMUS data in Section \ref{sec:primus}, we use \texttt{iSEDfit} to obtain the stellar masses and star formation rates for the SDSS-{\em GALEX} sample.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY SAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*} 
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{ccccccc} \hline \hline              
     &\multicolumn{1}{c}{$n_{\rm{env}}$}        & \multicolumn{2}{c}{$N_{\rm{gal}}$}  & \multicolumn{2}{c}{$\mathcal{M}_{\rm{lim}}$} & $M_{\rm{r}, lim}$ \\ 
    & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
$0.05 < z < 0.12$ & $n_{\rm{env}} < \lowenvthresh $ & 6533 & 7508 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.95 \\
               & $n_{\rm{env}} > \highenvthresh $ &14673 & 9717 &                          \\ 
                              & all          &$33553$                       & $29864$                          \\ \hline
$0.2 < z < 0.4$      &$n_{\rm{env}} < \lowenvthresh $           &363                    &1231 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.03 \\
               &$n_{\rm{env}} > \highenvthresh $            &379                    &756                           \\
               & all                & $1086$                      & $2879$                          \\ \hline
$0.4 < z < 0.6$      &$n_{\rm{env}} < \lowenvthresh $           &536                       &1498 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -20.98 \\
               &$n_{\rm{env}} > \highenvthresh $            &490                       &854                           \\
               & all               & $1560$                      & $3577$                          \\ \hline
$0.6 < z < 0.8$      &$n_{\rm{env}} < \lowenvthresh $           &567                       &1254  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.97 \\
               &$n_{\rm{env}} > \highenvthresh $            &498                       &671                           \\
               & all              & $1668$                      & $2964$                          \\ \hline
Total &      & \multicolumn{2}{c}{77151} & \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Number of galaxies ($N_{\rm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}). The subsamples are classified based on environment ($n_{\rm{env}}$) and star formation rate (star-forming or quiescent). The lowest redshift bin is derived from SDSS; the rest are from PRIMUS. We also list the stellar mass completeness limit, $\mathcal{M}_{\rm{lim}}$, for our sample along with the $r$-band absolute magnitude limits, $M_{\rm{r}, lim}$, for the Environment Defining Population. 
    \bigskip
\end{table*}

@@

For the PRIMUS objects that meet the above criteria, we assign statistical weights (described in \citealt{Coil:2011aa} and \citealt{Cool:2013aa}) in order to correct for targeting incompleteness and redshift failures. The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
as in Equation (1) in \cite{Moustakas:2013aa}.

Since we are ultimately interested in a mass complete galaxy sample to
derive SMFs and QFs, next we impose stellar mass completeness limits
to our galaxy sample.
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS are functions of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit. We use the same procedure as \cite{Moustakas:2013aa}, which follows \cite{Pozzetti:2010aa}, to empircally determine the stellar mass completeness limits. For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\log \; \mathcal{M}_{\mathrm{lim}} = \log \; \mathcal{M} + 0.4\;(m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields. We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins. In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies. Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (star-forming or quiescent classification is described in the following section). Finally, we use the polynomials to obtain the minimum stellar masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$, which are then used as PRIMUS stellar mass completeness limits.

@@

We now have a stellar mass complete sample derived from SDSS-{\em
  GALEX} and PRIMUS data. Since our sample is derived from two
different surveys, we account for the disparity in the redshift
uncertainty. While PRIMUS provides a large number of redshifts out to
$z = 1$, due to its use of a low dispersion prism, the redshift
uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
\%$) than that of the SDSS-{\em GALEX} redshifts. In order to have
comparable environment measures throughout our redshift range, we
apply PRIMUS redshift uncertainties to our galaxy sample selected from
SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
redshift by randomly sampling a Gaussian distribution with standard
deviation $\sigma = 0.005 (1+z_{\mathrm{SDSS}-GALEX})$, where
$z_{\mathrm{SDSS}-GALEX}$ is the redshift of the galaxy.

@@

\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 

>>>>

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael R.~Blanton\altaffilmark{1}, 
John~Moustakas\altaffilmark{2},
Alison L.~Coil\altaffilmark{3}, 
Richard J.~Cool\altaffilmark{4}, 
Daniel J.~Eisenstein\altaffilmark{5},
Ramin A.~Skibba\altaffilmark{3}
Kenneth C.~Wong\altaffilmark{6}, 
Guangtun~Zhu\altaffilmark{7}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{3}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{4}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of
the quiescent fraction ($f_{\mathrm{Q}}$) from $z =0.8 $ to $ 0.0$ using
spectroscopic redshifts and multi-wavelength imaging data from the
PRIsm MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey
(SDSS). Our stellar mass limited galaxy sample consists of $\sim
13,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS
galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent
or star-forming based on an evolving specific star formation cut, and
as low or high density environments based on fixed cylindrical
aperture environment measurements on a volume-limited environment
defining population. For quiescent and
star-forming galaxies in low or high density environments, we examine
the evolution of their stellar mass function (SMF). Then using the
SMFs we compute $f_{\mathrm{Q}}(\mathcal{M}_{*})$ and quantify its
evolution within our redshift range. We find that the quiescent
fraction is higher at higher masses and in denser environments. The
quiescent fraction rises with cosmic time for all masses and
environments. At a fiducial mass of $10^{10.5}M_\odot$, from $z\sim
0.7$ to $0.1$, the quiescent fraction rises by $15\%$ at the
lowest environments and by $25\%$ at the highest environments we measure.
These results suggest that for a minority of galaxies their cessation
of star formation is due to external influences on
them. However, in the recent Universe a substantial fraction of the
galaxies that cease forming stars do so due to internal processes.
\end{abstract}

@@

Throughout the paper we assume a cosmology with $\Omega_{m} = 0.3,
\Omega_{\Lambda} = 0.7$, and $H_0 = 70 \: \mathrm{km} \; \mathrm{s}^{-1}
\mathrm{Mpc}^{-1}$. All magnitudes are AB-relative.

@@

In Section \ref{sec:primus} and Section \ref{sec:sdss} we provide a
brief summary of the PRIMUS and SDSS data used for our sample
selection. In Section \ref{sec:target} we define our stellar mass complete galaxy sample.  
Then, in Section \ref{sec:sfq}, we classify the sample galaxies as quiescent or star-forming. 
We calculate the environment
using a volume-limited Environment Defining Population in Section
\ref{sec:environment}.  Finally, in Section \ref{sec:edgeeffect}, we
account for edge effects in the surveys.

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.2}
	\plotone{fig_edp_sdss_z0_05_0_12_primus_z0_2_1_0_Mr_redshift.png}
        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top. Both samples are divided into redshift bins: $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right). The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS. The rest contain galaxies and EDP selected from PRIMUS. The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies. Stellar mass completeness limits, described in Section \ref{sec:target}, are imposed on the galaxy population. Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRIMUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and
spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim
120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range
$z \approx 0-1.2$. The survey was conducted using the IMACS
spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers (\citealt{Coil:2011aa, Cool:2013aa}).

While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \mathrm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging for a total of $\sim 5.5 \; \mathrm{deg}^2$ (similar to the sample selection in \citealt{Moustakas:2013aa}). Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html}): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chandra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS). The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey field (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}). Our fifth and final field is the Cosmic Evolution Survey (COSMOS\footnote{http://cosmos.astro.caltech.edu}) field. For all of our fields we have near-UV (NUV) and far-UV (FUV) photometry from the {\em GALEX} Deep Imaging Survey (DIS; \citealt{Martin:2005aa, Morrissey:2005aa}) as well as ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs. \cite{Moustakas:2013aa} provides detailed descriptions of integrated flux calculations in the photometric bands for each of our fields. Furthermore, we derive the {\em K-corrections} from the photometry using \texttt{K-correct} (v4.2; \citealt{Blanton:2007aa}).

Finally, using the spectroscopic redshift and broad wavelength photometry we apply \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies (\citealt{Moustakas:2013aa}). \texttt{iSEDfit} uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}. For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \mathrm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SDSS-GALEX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SDSS-GALEX} \label{sec:sdss}
At low redshifts, we use spectroscopic redshifts and $ugriz$ photometry from the SDSS Data Release 7 (DR7; \citealt{Abazajian:2009aa}). More specifically we select galaxies from the New York University Value-Added Galaxy Catalog (hereafter VAGC) that satisfy the main sample criterion and have galaxy extinction corrected Petrosian magnitudes $14.5 < r < 17.6$ and spectroscopic redshifts within $0.01 < z < 0.2$ (\citealt{Blanton:2005aa}). We further restrict the VAGC sample to only galaxies with medium depth observations with total exposure time greater than $1 \; \mathrm{ks}$ from {\em GALEX} Release 6. This leaves $167,727$ galaxies.

Next, we use the MAST/CasJobs\footnote{http://galex.stsci.edu/casjobs} interface and a $4''$ diameter search radius, to obtain the NUV and FUV photometry for the SDSS-{\em GALEX} galaxies. For optical photometry, we use the $ugriz$ bands from the SDSS \texttt{model} magnitudes scaled to the $r$-band \texttt{cmodel} magnitude. These photometric bands are then supplemented with integrated $JHK_s$ magnitudes from the 2MASS Extended Source Catalog (XSC; \citealt{Jarrett:2000aa}) and with photometry at $3.4$ and $4.6 \mu \mathrm{m}$ from the WISE All-Sky Data Release\footnote{http://wise2.ipac.caltech.edu/docs/release/allsky}. Further details regarding the SDSS-{\em GALEX} sample photometry can be found in Section 2.4 of \cite{Moustakas:2013aa}. As previously done on the PRIMUS data in Section \ref{sec:primus}, we use \texttt{iSEDfit} to obtain the stellar masses and star formation rates for the SDSS-{\em GALEX} sample.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY SAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*} 
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{ccccccc} \hline \hline              
     &\multicolumn{1}{c}{$n_{\mathrm{env}}$}        & \multicolumn{2}{c}{$N_{\mathrm{gal}}$}  & \multicolumn{2}{c}{$\mathcal{M}_{\mathrm{lim}}$} & $M_{\mathrm{r}, lim}$ \\ 
    & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
$0.05 < z < 0.12$ & $n_{\mathrm{env}} < \lowenvthresh $ & 6533 & 7508 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.95 \\
               & $n_{\mathrm{env}} > \highenvthresh $ &14673 & 9717 &                          \\ 
                              & all          &$33553$                       & $29864$                          \\ \hline
$0.2 < z < 0.4$      &$n_{\mathrm{env}} < \lowenvthresh $           &363                    &1231 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.03 \\
               &$n_{\mathrm{env}} > \highenvthresh $            &379                    &756                           \\
               & all                & $1086$                      & $2879$                          \\ \hline
$0.4 < z < 0.6$      &$n_{\mathrm{env}} < \lowenvthresh $           &536                       &1498 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -20.98 \\
               &$n_{\mathrm{env}} > \highenvthresh $            &490                       &854                           \\
               & all               & $1560$                      & $3577$                          \\ \hline
$0.6 < z < 0.8$      &$n_{\mathrm{env}} < \lowenvthresh $           &567                       &1254  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.97 \\
               &$n_{\mathrm{env}} > \highenvthresh $            &498                       &671                           \\
               & all              & $1668$                      & $2964$                          \\ \hline
Total &      & \multicolumn{2}{c}{77151} & \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Number of galaxies ($N_{\mathrm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}). The subsamples are classified based on environment ($n_{\mathrm{env}}$) and star formation rate (star-forming or quiescent). The lowest redshift bin is derived from SDSS; the rest are from PRIMUS. We also list the stellar mass completeness limit, $\mathcal{M}_{\mathrm{lim}}$, for our sample along with the $r$-band absolute magnitude limits, $M_{\mathrm{r}, lim}$, for the Environment Defining Population. 
    \bigskip
\end{table*}

@@

For the PRIMUS objects that meet the above criteria, we assign statistical weights (described in \citealt{Coil:2011aa} and \citealt{Cool:2013aa}) in order to correct for targeting incompleteness and redshift failures. The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\mathrm{target}} \times f_{\mathrm{collision}} \times f_{\mathrm{success}})^{-1},
\end{equation}
as in Equation (1) in \cite{Moustakas:2013aa}.

Since we are ultimately interested in a mass complete galaxy sample to
derive SMFs and QFs, next we impose stellar mass completeness limits
to our galaxy sample.
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS are functions of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit. We use the same procedure as \cite{Moustakas:2013aa}, which follows \cite{Pozzetti:2010aa}, to empircally determine the stellar mass completeness limits. For each of the target galaxies we compute $\mathcal{M}_{\mathrm{lim}}$ using $\log \; \mathcal{M}_{\mathrm{lim}} = \log \; \mathcal{M} + 0.4\;(m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\mathrm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\mathrm{lim}}$ is the magnitude limit for our five fields. We construct a cumulative distribution of $\mathcal{M}_{\mathrm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins. In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies. Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (star-forming or quiescent classification is described in the following section). Finally, we use the polynomials to obtain the minimum stellar masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$, which are then used as PRIMUS stellar mass completeness limits.

@@

We now have a stellar mass complete sample derived from SDSS-{\em
  GALEX} and PRIMUS data. Since our sample is derived from two
different surveys, we account for the disparity in the redshift
uncertainty. While PRIMUS provides a large number of redshifts out to
$z = 1$, due to its use of a low dispersion prism, the redshift
uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
\%$) than the uncertainties of the SDSS-{\em GALEX} redshifts. In order to have
comparable environment measures throughout our redshift range, we
apply PRIMUS redshift uncertainties to our galaxy sample selected from
SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
redshift by randomly sampling a Gaussian distribution with standard
deviation $\sigma = 0.005 (1+z_{\mathrm{SDSS}-GALEX})$, where
$z_{\mathrm{SDSS}-GALEX}$ is the redshift of the galaxy.

@@

\mathrm{log}(\mathrm{SFR}_{\mathrm{min}}) = -0.49 + 0.64 \mathrm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
